Title

### 2013-03-05 inc/extension/initial_conditions/initial_conditions.tex
more andreas changes

We recognize that these initial conditions for an electron pulse generated by a laser-driven DC gun are idealized in that they neglect several important effects; in particular, the interplay of dispersive ($ \eta_{i}(0) \neq 0 $) and space-charge effects in the acceleration region of the photoelectron gun and transverse and longitudinal effects due to the divergence of the DC field in the vicinity of the gun anode.\cite{berger_dc_2009,togawa_ceb6_2007}
Such effects and the limits of the validity of \ref{eq:initial_sigma_z}, within the context of the AG model, will be presented elsewhere as they require \textit{a priori} this presented extension of the AG model.
However, \ref{eq:summary} also represent a defined set of initial conditions that allows the effect of electron optics (i.e., magnetic lenses and RF cavities) on electron pulse propagation to be more readily understood.
Moreover, they reflect the fact that the majority of DC photoelectron guns are driven by laser pulses with spatial and temporal profiles that are close to Gaussian.\cite{williamson_clocking_1997,sciaini_electronic_2009}
Only for specialized cases, such as the generation of uniform ellipsoid electron bunch shapes, is spatial and temporal manipulation of the incident laser pulse considered.\cite{luiten_how_2004,li_generating_2008}

@@

To test the validity of the simplistic model presented above I also designed a bin model that depends on nothing other than basic physics and a ``transmission'' function.
This function represents the likelihood of emission versus emission energy; the maximum energy being the full excess photoemission energy $\Delta E$.

In the model the space in front of the photocathode is binned into segments in ranges of distance from the photocathode.
The laser pulse duration is then binned into slices of time for a total duration of $N \tau$ where the peak of the pulse occurs at $N \tau / 2$; $N$ is a number selected to accumulate enough of the total laser pulse for an accurate simulation.
For each slice of time, one can determine the relative number of electrons generated in that slice (normalized to the total number that will be created by the end of the simulation), and the velocity distribution of those electrons.
Knowing the remaining time in the simulation and the acceleration due to the electric field, the velocity distribution can be used to place these electrons into final spatial bins.
Additionally, as the electrons are placed into these bins, their average velocity is stored as well.

This process repeats for each time slice until the finish time, at which point the laser has essentially stopped creating electrons.
At this time, the earliest fastest electrons will be a distance 
\begin{equation}
  d_{max} = v_0 N \tau + \frac{e E_{ DC }}{2 m} (N \tau)^2 
\end{equation}
away from the the photocathode, and the the electrons created in the last slice will be at $d=0$.
By counting the electrons in each spatial bin and fitting to a gaussian, we can determine $\sigma_z(0)$, the inital spatial uncertainty in the pulse.
Taking a weighted average of the velocity of the electrons in each spatial bin and fitting to a linear function across the pulse (as allowed by the AG model), we can determine the velocity (momentum) chirp $\gamma_z(0)$.
As seen in \ref{fig:bin_model}, the shapes of the actual output compare well with the fitted functional form for both of these parameters for all reasonable ranges of field and laser pulse duration.

>>>>

We recognize that these initial conditions for an electron pulse generated by a laser-driven DC gun are idealized in that they neglect several important effects; in particular, the interplay of dispersive ($ \eta_{i}(0) \neq 0 $) and space-charge effects in the acceleration region of the photoelectron gun and transverse and longitudinal effects due to the divergence of the DC field in the vicinity of the gun anode.\cite{berger_dc_2009,togawa_ceb6_2007}
Such effects and the limits of the validity of \ref{eq:initial_sigma_z}, within the context of the AG model, will be presented in Section \ref{sec:bin_model}.
However, \ref{eq:summary} also represent a defined set of initial conditions that allows the effect of electron optics (i.e., magnetic lenses and RF cavities) on electron pulse propagation to be more readily understood.
Moreover, they reflect the fact that the majority of DC photoelectron guns are driven by laser pulses with spatial and temporal profiles that are close to Gaussian.\cite{williamson_clocking_1997,sciaini_electronic_2009}
Only for specialized cases, such as the generation of uniform ellipsoid electron bunch shapes, is spatial and temporal manipulation of the incident laser pulse considered.\cite{luiten_how_2004,li_generating_2008}

@@

To test the validity of the simplistic model presented above, I also developed a bin model that depends on nothing other than basic Newtonian kinematics and a simple quantum-mechanical ``transmission'' function over a barrier.
This function represents the likelihood of emission versus emission energy; the maximum energy being the full excess photoemission energy $\Delta E$.

In the model, the space in front of the photocathode is binned into segments in ranges of distance from the photocathode.
The total laser pulse duration is then binned into slices of time for a total duration of $N \tau$, a few times the HW1/eM duration $\tau$; $N$ is a number selected to accumulate enough of the total laser pulse for an accurate simulation.
In this notation the peak of the pulse occurs at time $N \tau / 2$.
For each slice of time, one can determine the relative number of electrons generated in that slice (normalized to the total number that will be created by the end of the simulation), and the velocity distribution of those electrons.
Knowing the remaining time in the simulation and the acceleration due to the electric field, the velocity distribution can be used to place these electrons into their final spatial bins (ignoring Coulomb repulsion on these short time scales).
Additionally, as the electrons are placed into these bins, their average velocity is stored as well.

This simulation repeats for each time slice until the finish time, at which point the laser has essentially stopped creating electrons.
At this time, the earliest fastest electrons will be a distance 
\begin{equation}
  z_{max} = v_0 N \tau + \frac{e E_{ DC }}{2 m} (N \tau)^2 
\end{equation}
away from the the photocathode, and the the electrons created in the last slice will be at $z=0$.
By counting the electrons in each spatial bin and fitting to a gaussian, we can determine $\sigma_z(0)$, the inital spatial uncertainty in the pulse.
Taking a weighted average of the velocity of the electrons in each spatial bin and fitting to a linear function across the pulse (as allowed by the AG model), we can determine the velocity (momentum) chirp $\gamma_z(0)$.
As seen in \ref{fig:bin_model}, the shapes of the actual output compare well with the fitted functional form for both of these parameters for all reasonable ranges of field and laser pulse duration.
